---
title: "OcularPluseStudy_repeatability"
author: 
  - name: Sichao Wang
    email: wangsic1@msu.edu
    affiliations: 
      - name: Michigan State University, Center for Statistical Training and Consulting
date: "`r format(Sys.time(), '%Y-%m-%d, %H:%M:%S %Z')`"
format: 
  html: 
    toc: true 
    toc-depth: 4
    toc-location: left 
    number-sections: true
    number-depth: 4
    code-fold: false 
    code-tools: false 
    embed-resources: true 
    theme: default 
execute: 
  eval: true 
  echo: false #fenced
  output: true 
  message: false 
  warning: false 
  error: false 
  include: true 
---

# Project Overview:

Title: OcularPluseStudy_repeatability

<p>

Project PI's:

<p>

- András M. Komáromy 

<p>


CSTAT Personnel:

<p>

-   Sichao Wang, Ph.D.,

<p>



<h3>Primary Objective:</h3>

<p>

**Calculate repeatibiilty statistcs and ploting** 
<p>


## Project Updates:





```{r}
#| label: load-packages
#| include: false

pacman::p_load(## file folder setup
               fs,   # creat folder dir_create()
               here, # easy to do cross reference in the project.
               ## Data step
               readr,
               readxl, # read_excel()
               tidyverse,
               janitor,
               ## IDA
               Hmisc,
               ## Model
               meta,
               metafor,
               dmetar, #for find.outliers()
               lme4,
               glmmTMB,
               broom,
               emmeans,
               ##repeatibility
               irr,# for agreement
               psych,# for agreement
               confintr,#for ci_cor()
               DescTools,
               ## result reporting
               ### graph
               ggplot2,
               ### table
               gt,
               gtsummary,
               knitr,        # for kable()
               sjPlot      # tab_model()
               )


set.seed(42004063)

```

```{r}
#| label: setup-folder
#| include: false

# create the default folder/subfolder

dir_create(here("Data"))  # store raw data, clean data. 
dir_create(here("Data/Raw"))  
dir_create(here("Data/Clean")) 

dir_create(here("Documents"))  # all the docs
dir_create(here("Code"))       # r code
dir_create(here("E-mails"))    # correspondence

# Declare location of this script relative to the project root directory.
here::i_am(path = "Code/OcularPluseStudy_repeatability.qmd")  #save the qmd under code first and run this line.

# dir_ls()    # briefly check
# dir_tree()  # Show the tree, not necessary, takes time.
# dir_tree("Data")

```

```{r}
#| label: import-data
#| include: false

## Use gender as an example first.

dat_repeat <- read_excel(here("Data/Raw/Copy of OcularPulseStudy_Repeatability 9-1-23.xlsx"), 
    sheet = "Repeatability-2", skip = 3,na="x") %>% 
  clean_names() %>% 
  rename(eye_order="x1_od_first_2_os_first",od_opa="od_17",os_opa="os_18") %>% 
  select(session,animal_id,sex,dob,disease_state,eye_order,od_opa,os_opa)


dat_repeat_wide<-dat_repeat %>% pivot_longer(cols = ends_with("opa"),
                            names_to = c("eye",".value"),
                            names_pattern = "(.*)_(.*)",
    values_to = "opa") %>% 
  pivot_wider(names_from = session,values_from = opa)

```

#  Some agreement index

<<<<<<< HEAD
1. The repeatability coefficient (RC) is a number that, if you make two measurements of the same thing under the same conditions, the difference between those two measurements will be less than the RC in 95% of cases.[4, 5] The smaller the repeatability coefficient is, the better.

2. The calculation of Coefficient of Variation (CV) from duplicate measurements made on a number of different subjects or materials is used to determine the reproducibility of the measurements as an alternative to making a large number of observations on a single subject or material to estimate the within-run imprecision directly (Jones & Payne, 1997). There are three ways to calculate.

- Root mean square method
- Logarithmic method
- Within-subject standard deviation method
=======
The repeatability coefficient (RC) is a number that, if you make two measurements of the same thing under the same conditions, the difference between those two measurements will be less than the RC in 95% of cases.[4, 5] The smaller the repeatability coefficient is, the better.
>>>>>>> 166f083f674e6eb2ee88a4b8896d2451523ae736

```{r}
#| label: repeatability_coef

# https://rowannicholls.github.io/R/statistics/agreement/repeatability_coefficient.html

# https://cran.r-project.org/web/packages/rptR/vignettes/rptR.html  #for diff icc from model

<<<<<<< HEAD
dat_repeat_wide <- dat_repeat_wide %>% mutate(var = apply(.[(7:8)],1,var),m=apply(.[(7:8)],1,mean)) %>% mutate(CoV=sqrt(var)/m, CoVrm=((`1`-`2`)/(`1`/2+`2`/2))*((`1`-`2`)/(`1`/2+`2`/2)),sl=(log(`1`)-log(`2`))^2,SqrD=(`1`-`2`)^2)
=======
dat_repeat_wide <- dat_repeat_wide %>% mutate(var = apply(.[(7:8)],1,var),m=apply(.[(7:8)],1,mean)) %>% mutate(CoV=sqrt(var)/m)
>>>>>>> 166f083f674e6eb2ee88a4b8896d2451523ae736


rc <- 1.96 * sqrt(2) *sqrt(mean(dat_repeat_wide$var,na.rm=T))

CoVavg <- mean(dat_repeat_wide$CoV,na.rm=T)

<<<<<<< HEAD

#https://www.medcalc.org/manual/cvfromduplicates.php

#Root mean square method

# where d is the difference between two paired measurements and m is the mean of paired measurements.
# 
# The Root mean square method cannot be used when the mean of one or more pairs of measurements is 0.
# 
# For the calculation of the 95% Confidence Interval see Bland, 2006.

CoVrqrt<- sqrt(sum(dat_repeat_wide$CoVrm,na.rm = T)/(2*34))


#Logarithmic method
# In this method (Bland & Altman, 1996; Bland, 2006), first the sum of squared differences between the logarithms of observations is calculated:



CoVln <- exp(sqrt(sum(dat_repeat_wide$sl,na.rm = T)/(2*34))-1)

# Within-subject standard deviation method

# The Within-subject standard deviation method cannot be used when the overall mean of measurements is 0.
CoVwi <- sqrt(sum(dat_repeat_wide$SqrD,na.rm = T)/(2*34))/mean(dat_repeat_wide$m,na.rm=T)

data.frame(Index=c("repeatability coefficient (RC)","Coefficient of Variation (CV):Root mean square method","Coefficient of Variation (CV):Logarithmic method","Coefficient of Variation (CV): Within-subject standard deviation method"),estimate=c(rc,CoVrqrt,CoVln,CoVwi)) %>% gt()

# print(rc)
```


# Some agreement index

```{r}
#| label: tbl-ICC
#| tbl-cap: Agreement index table

opaICC <- icc(na.omit(dat_repeat_wide[,c("1","2")]),model = "twoway",type = "consistency",unit="single")




opaCor <- ci_cor(dat_repeat_wide[,c("1","2")], type = "bootstrap",  method = c("pearson"),R = 1000)



opaCCC<-CCC(dat_repeat_wide$`1`,dat_repeat_wide$`2`, ci = "z-transform", conf.level = 0.95, na.rm = TRUE)




data.frame(ICC=c(opaICC$value, opaICC$lbound,opaICC$ubound),Cor=c(opaCor$estimate,opaCor$interval),CCC=c(opaCCC$rho.c %>% unlist() %>% pluck(1), opaCCC$rho.c %>% unlist() %>% pluck(2),opaCCC$rho.c %>% unlist() %>% pluck(3))) %>% t() %>% data.frame() %>% rownames_to_column() %>% set_names("Agreement Index","Estimate","95% confidence interval(lower bound)","95% confidence interval(upper bound)") %>% gt()



```


@tbl-ICC shows some extra aggreement index.

ICC represents intraclass correlation
Cor represents regular pearson correlation
CCC represents concordance correlation coefficient

